Exploring probability distributions for bivariate temporal granularities

### 2019-11-29 main.Rmd
changing notation of quasi-periodic

\begin{equation} \label{eq:eq2}
C_{BG, G}(z) = BG(z\mod k(BG,G)) \forall z \in \mathbb{Z}^+,
BG(z) \neq \phi,
\end{equation}
where,  
z denotes the index set, 
BG denotes the index of the tsibble (bottom granularity), 
G be a linear granularity, periodic with respect to BG,     
k(BG,G) be the period length of the bottom granularity with respect to linear granularity G.  
\end{timedom}

@@

Table \ref{tab:definitions} shows representation of circular granularities relating two linear granularities. It is possible that none of these two linear granularities are bottom granularities. But the representation of the resultant circular granularity will be a function of the bottom granularity. For example, suppose the bottom granularity is minutes, and let $k_i$ is the period length of $C_i$.

@@

An **Aperiodic granularity** can not be defined using modular arithmetic. The modulus for these type of calendar categorizations are not constant due to irregular mapping with bottom granularities. For example,\autoref{tab:aperiodic} shows some example of aperiodic granularities ($A_i$) and plausible choices of period lengths($k_i$). The coarse granularity is assumed as the period within which the finer granularity will repeat its behavior aperiodically.

@@

Day-of-Month: & $A_1(z)$ &  $k_1=31, 30, 29, 28$\\
Hour-of-Month: & $A_2(z)$ & $k_2=24*31, 24*30, 24*29, 24*28$\\
Day-of-Year: & $A_3(z)$ & $k_3=366, 365$\\
Week-of-Month: & $A_4(z)$ & $k_4=5, 4$\\ 
\bottomrule
\end{tabular}
\end{center}
\caption{Illustrative aperiodic circular granularities with potential period lengths}
\label{tab:aperiodic}
\end{table}

**Definition: Aperiodic granularity** An aperiodic granularity A(AG, BG) that relates linear granularities AG and bottom granularity BG, with AG being periodical with respect to BG, is given by

\begin{equation}\label{eq:eq3}
A_{BG, AG}(z) = BG(z - \sum_{w=0}^{k-1}\vert T_{w \mod R'} \vert), z \in T_k
\end{equation}
where,  
z denotes the index set (index of BG),
$R'$ denotes the number of granules of AG in each period of BG,  
$T_w$ are the sets of indices of BG describing $AG(w)$ such that $AG(w) = \bigcup_{z \in T_w}BG(z)$, and $T_w = 0$ for $w \epsilon Z_{<0}$  
$\vert T_w \vert$ is the cardinality of set $T_w$.

Since AG is periodical with respect to BG, from definition of "Groups periodically into" the following holds true:

- $BG \trianglelefteq AG,$
- $AG(w) = \bigcup_{z \in T_w \mod R}BG(P'*\lfloor w/R' \rfloor + z)$,  where P' denotes the period of the granularity BG.

>>>>

\begin{equation} \label{eq:eq2}
C_{BG, G}(z) = BG(z\mod k(BG,G)) \forall z \in \mathbb{Z}^+,
BG(z) \neq \phi,
\end{equation}
where,  
z denotes the index set, 
BG denotes the index of the tsibble (bottom granularity), 
G be a linear granularity, periodic with respect to BG,     
and k(BG,G) be the period length of the bottom granularity with respect to linear granularity G. Here, linear granularities BG and G has regular mapping.
\end{timedom}

@@

Table \ref{tab:definitions} shows representation of circular granularities relating two linear granularities. It is possible that none of these two linear granularities are bottom granularities. But the representation of the resultant circular granularity will be a function of the bottom granularity. For example, suppose the bottom granularity is minutes, and let $k_i$ is the number of granules in each granule of $C_i$, also referred to as the period length.

@@

A **quasi-circular granularity** can not be defined using modular arithmetic due to its irregular mapping with the bottom granularity. For example, \autoref{tab:aperiodic} shows some example of quasi-circular granularities ($QC_i$) and plausible choices of number of granules of the finer granularity inside each granule of the coarser one($k_i$).

@@

Day-of-Month: & $QC_1(z)$ &  $k_1=31, 30, 29, 28$\\
Hour-of-Month: & $QC_2(z)$ & $k_2=24*31, 24*30, 24*29, 24*28$\\
Day-of-Year: & $QC_3(z)$ & $k_3=366, 365$\\
Week-of-Month: & $QC_4(z)$ & $k_4=5, 4$\\ 
\bottomrule
\end{tabular}
\end{center}
\caption{Illustrative aperiodic circular granularities with potential period lengths}
\label{tab:aperiodic}
\end{table}

\begin{timedom}\label{def:circular}
A quasi-circular granularity QC_(BG, G) that relates linear granularities G and bottom granularity BG, with AG being periodical with respect to BG, is given by

\begin{equation}\label{eq:eq3}
QC_{BG, G}(z) = BG(z - \sum_{w=0}^{k-1}\vert T_{w \mod R'} \vert), z \in T_k
\end{equation}
where,  
z denotes the index set (index of BG),
$R'$ denotes the number of granules of G in each period of the grouping (BG,G),   
$T_w$ are the sets of indices of BG describing $G(w)$ such that $G(w) = \bigcup_{z \in T_w}BG(z)$,$T_w = 0$ for $w \epsilon Z_{<0}$ and $\vert T_w \vert$ is the cardinality of set $T_w$. Here, linear granularities BG and G has irregular mapping.
\end{timedom}

Since G is periodical with respect to BG, from definition of "Groups periodically into" the following holds true:

- $BG \trianglelefteq G,$
- $G(w) = \bigcup_{z \in T_w \mod R}BG(P'*\lfloor w/R' \rfloor + z)$,  where P' denotes the period of the granularity BG.
